Scattering from compact objects: \\ Regge poles and the Complex Angular Momentum method

### 2019-12-16 rainbowCAM.tex

Next, we examine the role of Regge poles in the time-independent scattering of monochromatic planar waves. We apply Complex Angular Momentum techniques to re-sum the partial wave series for the scattering amplitude, expressing it as a residue series evaluated at poles in the first quadrant, accompanied by a background integral. We compute the scattering cross section at several frequencies, and show precise agreement with the partial-wave calculations. Finally, we show that compact bodies naturally give rise to orbiting, glory, and rainbow-scattering interference effects.
\end{abstract}

@@

The CAM theory was originally developed to deal theoretically with the propagation and diffraction of radio waves around the Earth, by Watson~\cite{Watson18} (see also the work of Sommerfeld~\cite{Sommerfeld49}). It has since been extensively used in several domains of physics involving resonant scattering theory (see, e.g., Refs.~\cite{deAlfaro:1965zz,Newton:1982qc,Watson18,Sommerfeld49,Nussenzveig:2006,Grandy2000,Uberall1992,AkiRichards2002,AkiRichards2002,Gribov69,
Collins77,BaronePredazzi2002,DonnachieETAL2005} as well as references therein for various applications in quantum mechanics, nuclear physics, electromagnetism, optics, seismology and high energy physics). Since the pioneering work in 1994 by Andersson and Thylwe~\cite{Andersson:1994rk,Andersson:1994rm} the CAM theory has been successfully applied to black hole scattering scenarios. They described the scattering of scalar waves by a Schwarzschild black hole using CAM techniques, and showed that, in this case, the Regge poles are associated with ``surface waves'' localised near the unstable light ring at $ r = 3M $ (\textit{i.e.}, the so-called photon sphere). Later, Decanini, Folacci and Jensen have shown that the complex frequencies of weakly damped QNMs are Breit-Wigner resonances generated by surface waves previously mentioned and, using the concept of Regge trajectories, they were able to construct semiclassically the spectrum of the QNM complex frequencies~\cite{Decanini:2002ha}. Recently, Folacci and Ould~El~Hadj have shown that CAM machinery can be used for precise numerical calculations of scattering cross sections of scalar fields, electromagnetic fields~\cite{Folacci:2019cmc} and gravitational waves~\cite{Folacci:2019vtt} on Schwarzschild space-time. Moreover, using the third WKB approximation to obtain the asymptotic expressions for the lowest Regge poles~\cite{Decanini:2009mu} and associated residues, they have able to provide an analytical approximation describing accurately both ``glory'' and large part of the ``orbiting'' oscillations in black hole scattering cross sections in the short-wavelength regime. An accurate approximation for the black hole absorption cross section has also been derived via an analysis of Regge poles~\cite{Decanini:2011xi,Decanini:2011xw}. In addition, an alternative description of gravitational radiation from black holes based on CAM theory was developed in Ref.~\cite{Folacci:2018sef}.

CAM techniques are yet to be fully applied to compact-body scattering, it appears, with one notable exception: in 1991, Chandrasekhar and Ferrari \cite{ChandrasekharIV:1992ey} examined the Regge pole spectra for relativistic stellar models.
Their study focussed on resonant modes (poles with small imaginary parts corresponding to trapped $w$-modes or fluid modes), and it employed CAM theory to calculate the flow of gravitational energy through a star. It seems reasonable to assume that CAM theory can aid a deeper understanding of scattering by other compact objects, such as neutron stars and UCOs, and this is our purpose herein.

There is a close relationship between Regge poles and quasi-normal modes (QNMs); both are sets of poles of the scattering matrix, with the latter lying in the complex-frequency plane. The excitation of black hole QNMs leads to distinctive signatures in \emph{time-dependent} scattering scenarios. For example, in the immediate aftermath of a black hole merger, the perturbed black hole returns to a quiescent state via a ``ringdown phase'' in which its gravitational-wave signal is well described as a sum of quasinormal modes \cite{Giesler:2019uxc}. The QNM spectrum of compact bodies have been well-studied by several authors  \cite{Detweiler:1985zz, Kokkotas:1986gd, Chandrasekhar449, Kokkotas:1992ka, Leins:1993zz, Andersson:1995ez, Andersson1996}, and are reviewed in Ref.~\cite{Kokkotas:1999bd}.

@@

A widely-studied model is that of a polytropic star, with an EoS $p(\rho) = \kappa \rho^{1+1/\hat{n}}$, where $\hat{n}$ is the polytropic index (see e.g.~\cite{Stratton:2019deq}). Here we shall consider a special case: an incompressible perfect fluid ball of uniform density described by Schwarzschild's interior solution for an incompressible fluid \cite{Shapiro1983}, with
\begin{subequations}
\begin{align}
\rho &= \frac{M}{\frac{4}{3} \pi R^3} , \\
p &= \rho \frac{\beta(R) - \beta(r)}{ \beta(r) - 3 \beta(R)} , \\
\beta(x) &= \sqrt{3 - 8 \pi \rho x^2}
\end{align}
\end{subequations}
and metric functions
%
\begin{subequations}\label{Interior_Solution}
\begin{align}\label{Interior_Solution_f}
 f(r) &= \frac{1}{4}\left(1-\frac{2 M r^2}{R^3}\right)+\frac{9}{4}\left(1-\frac{2M}{R}\right) \nn \\
       & \quad -\frac{3}{2} \sqrt{\left(1-\frac{2M}{R}\right)\left(1-\frac{2 M r^2}{R^3}\right)}, \\
 h(r) &= 1-\frac{2 M r^2}{R^3} . \label{Interior_Solution_h}
\end{align}
\end{subequations}
The constant-density model can be thought of as representing the $\hat{n} \rightarrow 0$ limit of the family of polytropes.
The radial function $h(r)$ is $C^0$ at the surface of the star $r=R$ (i.e.~continuous but not differentiable), and the radial function $f(r)$ is $C^1$ there (i.e.~once-differentiable).
For a general polytrope with $n>0$ and $m$ the smallest integer such that $m \geq n$, $h(r)$ is $C^m$ and $f(r)$ is $C^{m+1}$ at the surface.
As we shall see, the breakdown of smoothness leads to consequences for the Regge pole spectrum.

@@

\subsection{Effective potentials}\label{subsec:Potentials}
The effective potential for the scalar field in Eq.~(\ref{H_Radial_equation}) is $V_{\ell}(r) = V_{\ell}^{(s=0)}(r)$, where we define
\begin{equation}\label{Inside_Potentiel}
  V_{\ell}^{(s)}(r) \equiv f(r)\left[\frac{\ell(\ell+1)}{r^2}+\frac{\beta_s \, h(r)}{2r}\left(\frac{f'(r)}{f(r)}+\frac{h'(r)}{h(r)}\right)\right] ,
\end{equation}
where $\beta_s \equiv 1-s^2$.
Remarkably, the radial equation for axial gravitational perturbations is identical to Eq.~(\ref{H_Radial_equation}) but with an effective potential $V_{\ell}^{\text{ax}}(r)$ where \cite{Cardoso:2014sna}
\begin{eqnarray}\label{RW_Potentiel_axialGW}
V_{\ell}^{\text{ax}}(r) = V_{\ell}^{(s=2)} + 8 \pi f(r) (p - \rho)  .
\end{eqnarray}
%
Outside the star in the vacuum region ($r>R$), the effective potentials reduce to the Regge-Wheeler potential,
\begin{equation}\label{RW_Potentiel}
V^{(s)}_{\ell}(r) =\left(1-\frac{2M}{r}\right)\left(\frac{\ell(\ell+1)}{r^2}+\frac{2M \beta_s}{r^3}\right)
\end{equation}
with $s=0$ in the scalar-field case, and $s=2$ in the axial gravitational-wave case. In the exterior, the tortoise coordinates $r_\ast$ reduces to $r_\ast = r+ 2M \ln [r/(2M) -1]+k$, where $k$ is a constant that is chosen such that $r_\ast(r=0) = 0$ and $r_\ast(r)$ is a continuous function.

Effective potentials for the incompressible model are shown in Fig.~\ref{fig:Veff}, for two cases: (i) a neutron-star model with $R = 6M$, and (ii) a ultra-compact object (UCO \cite{Macedo:2018yoi}) with $R = 2.26M$. % (i.e.~close to the Buchdahl bound of $R/M = 9/4$).
In both cases we observe a discontinuity in $V_{\ell}(r)$ across the star's surface, due to the $C^0$ property of $h(r)$. The jump in the potential takes opposite signs in the scalar-field and gravitational-wave cases, with
\begin{subequations}
\begin{align}
\Delta V_{\ell}^{(s=0)} &= + \frac{3Mf(R)}{R^3} , \\
\Delta V_{\ell}^{\text{ax}} &= - \frac{3Mf(R)}{R^3} ,
\end{align}
\end{subequations}
where
\begin{equation}
\Delta V_{\ell} \equiv \lim_{\epsilon \rightarrow 0} \left\{ V_{\ell}(R + \epsilon) - V_{\ell}(R - \epsilon) \right\} . \label{def:DeltaV}
\end{equation}

 \begin{figure}[htb]
\centering
 \includegraphics[scale=0.50]{potentials_s02_CD_R6L2_v3} \\ \vspace{0.2cm}
 \includegraphics[scale=0.50]{potentials_s02_CD_R2p26L2_v3}
\caption{\label{RP_approx_2Mw_3_6_s_1} The effective potential $V_\ell$ for a quadrupole ($\ell =2$) perturbation of a compact body of constant density and tenuity $R/M = 6$ (upper) and $R /M = 2.26$ (lower). The scalar field potential (\ref{Inside_Potentiel}) and axial gravitational-wave potential (\ref{RW_Potentiel_axialGW}) are indicated as solid/black lines and dotted/red lines, respectively. The horizontal axis is the tortoise coordinate $r_\ast/(2M)$ defined in Eq.~(\ref{eq:tortoise}).}
\label{fig:Veff}
\end{figure}

@@

The \emph{quasinormal mode spectrum} is the set of frequencies $\{ \omega_{\ell n} \}$ in the complex-$\omega$ plane at which the scattering matrix $ S_{\ell}(\omega)$ has a simple pole for a integer value of $\ell$ (so $\ell \in \mathbb{N}$ and $\omega_{\ell n} \in \mathbb{C}$).

@@

The $w$-modes (quasinormal modes) may be divided into three branches:
	\begin{enumerate}
   \item Curvature modes, the standard $w$-modes extant for all relativistic stars. The less compact the star the more rapid the damping (Im$\{\omega\}$ increases with $R/M$).
   \item Interface modes ($\omega_{\text{II}}$-modes \cite{Leins:1993zz}), characterised by very rapid damping (i.e.~large negative imaginary part of $\omega_{\ell n}$). This branch of modes is somewhat similar to modes for acoustic waves scattered of a hard sphere.
   \item Trapped modes \cite{Chandrasekhar449}: These modes exist for UCOs with $R/M < 3$, because the effective radial potential has a local minimum inside the star, and local maximum near the photon sphere $r=3M$. %The trapped modes are essentially the first few curvature modes with energy less than the potential barrier.
   The number of trapped modes increases with the depth of the potential well, and the damping rate decreases.
	\end{enumerate}

@@

Leins, Nollert and Soffel \cite{Leins:1993zz} have developed a method for calculating the polar QNM frequencies of spherically symmetric spacetimes. Benhar, Berti and Ferarri (BBF) have extended this method to the axial sector. Here we shall present a generalisation the BBF method for axial \emph{and} scalar QNM frequencies ($s=2$ and $s=0$ respectively). The method is equally valid, \textit{mutatis mutandis}, for finding Regge poles $\{\lambda_n(\omega)= \ell_n +1/2\}$ of $ S_{\ell}(\omega)$.  The solution of the Regge-Wheeler equation is written in a power-series form as follows:
%
\begin{eqnarray}\label{Power_series}
% \nonumber % Remove numbering (before each equation)
 \phi_{\omega_\ell}(r)&=&\left(\frac{r}{2M}-1\right)^{i 2M\omega} \,e^{i\omega r} \sum_{n=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n \nonumber \\
                      &=& e^{i\omega r_*(r)}\sum_{n=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n
\end{eqnarray}
where $r = b$ is some point outside the star. By substituting \eqref{Power_series} in the Regge-Wheeler equation, it can be shown that the coefficients $a_n$ satisfy a four-term recurrence relation of the form:
\begin{equation}\label{Recurrence_4_terms}
\alpha_n a_{n+1} + \beta_n a_{n} +\gamma_{n} a_{n-1} +\delta_{n} a_{n-2}  = 0, \quad \forall n\geq 2
\end{equation}
where
\begin{subequations}
\begin{eqnarray}\label{Coeffs_3_termes}
 && \alpha_n = n (n+1)\left(1-\frac{2M}{b}\right)   \\
 && \beta_n  = 2i\omega b n + 3\left(\frac{2M}{b}\right)n^2-2n^2  \\
 && \gamma_n = \left(1-\frac{6M}{b}\right)n(n-1)-\frac{2M\beta_s}{b}-\ell(\ell+1)  \\
 && \delta_n = \left(\frac{2M}{b}\right)\left(n(n-2)+\beta_s\right)
\end{eqnarray}
\end{subequations}
To determine the initial conditions $a_0$ and $a_1$, we impose the continuity of $\phi_{\omega_\ell}(r)$ and its derivative in $r = b$, according to Eq~\eqref{Power_series}, we obtain:
\begin{eqnarray}\label{Initial_Conds}
 && a_0 = e^{i\omega r_*(b)\phi_{\omega_\ell}(b)}  \\
 && a_1 = b e^{-i\omega r_*(b)}\left(\frac{-i\omega b}{b-2M}\phi_{\omega_\ell}(b)+ \frac{d}{dr}\phi_{\omega_\ell}(r)\Big{|}_{r=b}\right)
\end{eqnarray}
Here, to obtain $\phi_{\omega_\ell}(b)$ and its derivative in $r=b$, we need to solve numerically the Eq.~\eqref{H_Radial_equation} inside the star and to continue the solution outside, up to $r=b$, by solving the Regge-wheeler equation.

It is important to note that, the \textit{continued fraction method} is applied to the three-term recurrence relation. To do this, Leins~\emph{et al.} and BBF use the method introduced by Leaver in
the case of Reissner-Nordst\"om black holes \cite{Leaver:1990zz}, \textit{i.e.}, reducing the four-term recurrence relations \eqref{Recurrence_4_terms} to a three-term recurrence relation by using the gaussian elimination step.

@@

Figure \ref{fig:rp1} shows the Regge pole spectrum for a neutron-star-like body ($R/M = 6$). We see that there are two branches of Regge poles in the first quadrant, which meet at $\text{Re}( \lambda_n(\omega) ) \sim \omega b_0$, where $b_0$ is the impact parameter for the null ray which grazes the surface of the compact body. The axial GW $s=2$ modes (filled markers) are typically close to their scalar-field $s=0$ counterparts (unfilled markers), as might be anticipated from the similarities in the effective potentials for the two cases (see Fig.~\ref{fig:Veff}).

@@

We can be confident that there are no additional branches of Regge poles in the first quadrant, for two reasons. First, we have scanned across the complex-$\lambda$ domains shown in Figs.~\ref{RP_R6_approx_2Mw_3_6_s_1} and \ref{RP_R226_approx_2Mw_3_6_s_1}, as detailed in Sec.~\ref{subsec:method}. Second, in our calculation of $d\sigma/d\Omega$, we find a precise numerical agreement between the CAM calculation and the partial-wave calculation; this would not be the case if poles in this domain had been missed.

>>>>

Next, we examine the role of Regge poles in the time-independent scattering of monochromatic planar waves. We apply Complex Angular Momentum techniques to re-sum the partial wave series for the scattering amplitude, expressing it as a residue series evaluated at poles in the first and fourth quadrants, accompanied by a background integral. We compute the scattering cross section at several frequencies, and show precise agreement with the partial-wave calculations. Finally, we show that compact bodies naturally give rise to orbiting, glory, and rainbow-scattering interference effects.
\end{abstract}

@@

The CAM theory was originally developed to deal theoretically with the propagation and diffraction of radio waves around the Earth, by Watson~\cite{Watson18} (see also the work of Sommerfeld~\cite{Sommerfeld49}). It has since been extensively used in several domains of physics involving resonant scattering theory (see, e.g., Refs.~\cite{deAlfaro:1965zz,Newton:1982qc,Watson18,Sommerfeld49,Nussenzveig:2006,Grandy2000,Uberall1992,AkiRichards2002,AkiRichards2002,Gribov69,
Collins77,BaronePredazzi2002,DonnachieETAL2005} as well as references therein for various applications in quantum mechanics, nuclear physics, electromagnetism, optics, seismology and high energy physics). Since the pioneering work in 1994 by Andersson and Thylwe~\cite{Andersson:1994rk,Andersson:1994rm} the CAM theory has been successfully applied to black hole scattering scenarios. They described the scattering of scalar waves by a Schwarzschild black hole using CAM techniques, and showed that, in this case, the Regge poles are associated with ``surface waves'' localised near the unstable light ring at $ r = 3M $ (\textit{i.e.}, the so-called photon sphere). Later, Decanini, Folacci and Jensen showed that the complex frequencies of weakly damped QNMs are Breit-Wigner resonances generated by the surface waves previously mentioned and, using the concept of Regge trajectories, they were able to construct semiclassically the spectrum of the QNM complex frequencies~\cite{Decanini:2002ha}. Recently, Folacci and Ould~El~Hadj have shown that CAM machinery can be used for precise numerical calculations of scattering cross sections of scalar fields, electromagnetic fields~\cite{Folacci:2019cmc} and gravitational waves~\cite{Folacci:2019vtt} on a Schwarzschild space-time. Moreover, using the third WKB approximation to obtain the asymptotic expressions for the lowest Regge poles~\cite{Decanini:2009mu} and associated residues, they have been able to provide an analytical approximation describing accurately both the ``glory'' and a large part of the ``orbiting'' oscillations in black hole scattering cross sections in the short-wavelength regime. An accurate approximation for the black hole absorption cross section has also been derived via an analysis of Regge poles~\cite{Decanini:2011xi,Decanini:2011xw}. In addition, an alternative description of gravitational radiation from black holes based on CAM theory was developed in Ref.~\cite{Folacci:2018sef}.

CAM techniques are yet to be fully applied to compact-body scattering, it appears, with one notable exception: in 1991, Chandrasekhar and Ferrari \cite{ChandrasekharIV:1992ey} examined the Regge pole spectra for relativistic stellar models.
Their study focussed on resonant modes (poles with small imaginary parts corresponding to trapped $w$-modes or fluid modes), and it employed CAM theory to calculate the flow of gravitational energy through a star. It seems reasonable to assume that CAM theory could lead to a deeper understanding of scattering by other compact objects, such as neutron stars and UCOs, and this is our purpose herein.

There is a close relationship between Regge poles and quasi-normal mode (QNM) frequencies; both are sets of poles of the scattering matrix, with the latter lying in the complex-frequency plane. The excitation of black hole QNMs leads to distinctive signatures in \emph{time-dependent} scattering scenarios. For example, in the immediate aftermath of a black hole merger, the perturbed black hole returns to a quiescent state via a ``ringdown phase'' in which its gravitational-wave signal is well described as a sum of quasinormal modes \cite{Giesler:2019uxc}. The QNM spectrum of compact bodies have been well-studied by several authors  \cite{Detweiler:1985zz, Kokkotas:1986gd, Chandrasekhar449, Kokkotas:1992ka, Leins:1993zz, Andersson:1995ez, Andersson1996}, and are reviewed in Ref.~\cite{Kokkotas:1999bd}.

@@

A widely-studied model is that of a polytropic star, with an EoS $p(\rho) = \kappa \rho^{1+1/\hat{n}}$, where $\hat{n}$ is the polytropic index (see e.g.~\cite{Stratton:2019deq}). Here we shall consider a special case: an incompressible perfect fluid ball of uniform density described by Schwarzschild's interior solution for an incompressible fluid \cite{Shapiro1983}, with
\begin{subequations}
\begin{align}
\rho &= \frac{M}{\frac{4}{3} \pi R^3} , \\
p &= \rho \frac{\beta(R) - \beta(r)}{ \beta(r) - 3 \beta(R)} , \\
\beta(x) &= \sqrt{3 - 8 \pi \rho x^2},
\end{align}
\end{subequations}
and metric functions
%
\begin{subequations}\label{Interior_Solution}
\begin{align}\label{Interior_Solution_f}
 f(r) &= \frac{1}{4}\left(1-\frac{2 M r^2}{R^3}\right)+\frac{9}{4}\left(1-\frac{2M}{R}\right) \nn \\
       & \quad -\frac{3}{2} \sqrt{\left(1-\frac{2M}{R}\right)\left(1-\frac{2 M r^2}{R^3}\right)}, \\
 h(r) &= 1-\frac{2 M r^2}{R^3} . \label{Interior_Solution_h}
\end{align}
\end{subequations}
The constant-density model can be thought of as representing the $\hat{n} \rightarrow 0$ limit of the family of polytropes.
The radial function $h(r)$ is $C^0$ at the surface of the star $r=R$ (i.e.~continuous but not differentiable), and the radial function $f(r)$ is $C^1$ there (i.e.~once-differentiable).
For a general polytrope with $\hat{n}>0$ and $m$ the smallest integer such that $m \geq \hat{n}$, $h(r)$ is $C^m$ and $f(r)$ is $C^{m+1}$ at the surface.
As we shall see, the breakdown of smoothness leads to consequences for the Regge pole spectrum.

@@

\subsection{Effective potentials}\label{subsec:Potentials}
The effective potential for the scalar field in Eq.~(\ref{H_Radial_equation}) is $V_{\ell}(r) = V_{\ell}^{(s=0)}(r)$, where we define
\begin{equation}\label{Inside_Potentiel}
  V_{\ell}^{(s)}(r) \equiv f(r)\left[\frac{\ell(\ell+1)}{r^2}+\frac{\beta_s \, h(r)}{2r}\left(\frac{f'(r)}{f(r)}+\frac{h'(r)}{h(r)}\right)\right] ,
\end{equation}
where $\beta_s \equiv 1-s^2$.
Remarkably, the radial equation for axial gravitational perturbations is identical to Eq.~(\ref{H_Radial_equation}) but with an effective potential $V_{\ell}^{\text{ax}}(r)$ where \cite{Cardoso:2014sna}
\begin{eqnarray}\label{RW_Potentiel_axialGW}
V_{\ell}^{\text{ax}}(r) = V_{\ell}^{(s=2)} + 8 \pi f(r) (p - \rho)  .
\end{eqnarray}
%
Outside the star in the vacuum region ($r>R$), the effective potentials reduce to the Regge-Wheeler potential,
\begin{equation}\label{RW_Potentiel}
V^{(s)}_{\ell}(r) =\left(1-\frac{2M}{r}\right)\left(\frac{\ell(\ell+1)}{r^2}+\frac{2M \beta_s}{r^3}\right)
\end{equation}
with $s=0$ in the scalar-field case, and $s=2$ in the axial gravitational-wave case. In the exterior, the tortoise coordinate $r_\ast$ reduces to $r_\ast = r+ 2M \ln [r/(2M) -1]+k$, where $k$ is a constant that is chosen such that $r_\ast(r=0) = 0$ and $r_\ast(r)$ is a continuous function.

Effective potentials for the incompressible model are shown in Fig.~\ref{fig:Veff}, for two cases: (i) a neutron-star model with $R = 6M$, and (ii) a ultra-compact object (UCO \cite{Macedo:2018yoi}) with $R = 2.26M$. % (i.e.~close to the Buchdahl bound of $R/M = 9/4$).
In both cases we observe a discontinuity in $V_{\ell}(r)$ across the star's surface, due to the discontinuity in the density $\rho$ (which implies the $C^0$ property of $h(r)$). The jump in the potential takes opposite signs in the scalar-field and gravitational-wave cases, with
\begin{subequations}
\begin{align}
\Delta V_{\ell}^{(s=0)} &= + \frac{3Mf(R)}{R^3} , \\
\Delta V_{\ell}^{\text{ax}} &= - \frac{3Mf(R)}{R^3} ,
\end{align}
\end{subequations}
where
\begin{equation}
\Delta V_{\ell} \equiv \lim_{\epsilon \rightarrow 0} \left\{ V_{\ell}(R + \epsilon) - V_{\ell}(R - \epsilon) \right\} . \label{def:DeltaV}
\end{equation}

 \begin{figure}[htb]
\centering
 \includegraphics[scale=0.50]{potentials_s02_CD_R6L2_v4} \\ \vspace{0.2cm}
 \includegraphics[scale=0.50]{potentials_s02_CD_R2p26L2_v4}
\caption{\label{RP_approx_2Mw_3_6_s_1} The effective potential $V_\ell$ for a quadrupole ($\ell =2$) perturbation of a compact body of constant density and tenuity $R/M = 6$ (upper) and $R /M = 2.26$ (lower). The scalar field potential - Eq.~(\ref{Inside_Potentiel}) - and axial gravitational-wave potential - Eq.~(\ref{RW_Potentiel_axialGW}) - are indicated as solid/black lines and dotted/red lines, respectively. The horizontal axis is the tortoise coordinate $r_\ast/(2M)$ defined in Eq.~(\ref{eq:tortoise}).}
\label{fig:Veff}
\end{figure}

@@

The \emph{quasinormal mode spectrum} is the set of frequencies $\{ \omega_{\ell n} \}$ in the complex-$\omega$ plane at which the scattering matrix $ S_{\ell}(\omega)$ has a simple pole for an integer value of $\ell$ (so $\ell \in \mathbb{N}$ and $\omega_{\ell n} \in \mathbb{C}$).

@@

The $w$-modes (quasinormal modes) may be divided into three branches:
	\begin{enumerate}
   \item Curvature modes, the standard $w$-modes extant for all relativistic stars. The less compact the star the more rapid the damping (Im$\{\omega\}$ increases with $R/M$).
   \item Interface modes ($\omega_{\text{II}}$-modes \cite{Leins:1993zz}), characterised by very rapid damping (i.e.~large negative imaginary part of $\omega_{\ell n}$). This branch of modes is somewhat similar to modes for acoustic waves scattered of a hard sphere.
   \item Trapped modes \cite{Chandrasekhar449}: These modes may exist when the effective radial potential has a cavity region, which is the case for UCOs ($R/M < 3$). %The trapped modes are essentially the first few curvature modes with energy less than the potential barrier.
   The number of trapped modes increases with the depth of the potential well, and the damping rate decreases.
	\end{enumerate}

@@

Leins, Nollert and Soffel \cite{Leins:1993zz} have developed a method for calculating the polar QNM frequencies of spherically symmetric spacetimes. Benhar, Berti and Ferarri (BBF) have extended this method to the axial sector. Here we shall present a generalisation of the BBF method for axial \emph{and} scalar QNM frequencies ($s=2$ and $s=0$ respectively). The method is equally valid, \textit{mutatis mutandis}, for finding Regge poles $\{\lambda_n(\omega)= \ell_n +1/2\}$ of $ S_{\ell}(\omega)$.  The solution of the Regge-Wheeler equation is written in a power-series form as follows:
%
\begin{eqnarray}\label{Power_series}
% \nonumber % Remove numbering (before each equation)
 \phi_{\omega_\ell}(r)&=&\left(\frac{r}{2M}-1\right)^{i 2M\omega} \,e^{i\omega r} \sum_{n=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n \nonumber \\
                      &=& e^{i\omega r_*(r)}\sum_{n=0}^{+\infty}a_n\left(1-\frac{b}{r}\right)^n
\end{eqnarray}
where $r = b$ is some point outside the star. By substituting \eqref{Power_series} in the Regge-Wheeler equation, it can be shown that the coefficients $a_n$ satisfy a four-term recurrence relation of the form:
\begin{equation}\label{Recurrence_4_terms}
\alpha_n a_{n+1} + \beta_n a_{n} +\gamma_{n} a_{n-1} +\delta_{n} a_{n-2}  = 0, \quad \forall n\geq 2
\end{equation}
where
\begin{subequations}
\begin{eqnarray}\label{Coeffs_3_termes}
 && \alpha_n = n (n+1)\left(1-\frac{2M}{b}\right)   \\
 && \beta_n  = 2i\omega b n + 3\left(\frac{2M}{b}\right)n^2-2n^2  \\
 && \gamma_n = \left(1-\frac{6M}{b}\right)n(n-1)-\frac{2M\beta_s}{b}-\ell(\ell+1)  \\
 && \delta_n = \left(\frac{2M}{b}\right)\left(n(n-2)+\beta_s\right)
\end{eqnarray}
\end{subequations}
To determine the initial conditions $a_0$ and $a_1$, we impose the continuity of $\phi_{\omega_\ell}(r)$ and its derivative in $r = b$, according to Eq~\eqref{Power_series}, we obtain:
\begin{eqnarray}\label{Initial_Conds}
 && a_0 = e^{i\omega r_*(b)\phi_{\omega_\ell}(b)}  \\
 && a_1 = b e^{-i\omega r_*(b)}\left(\frac{-i\omega b}{b-2M}\phi_{\omega_\ell}(b)+ \frac{d}{dr}\phi_{\omega_\ell}(r)\Big{|}_{r=b}\right)
\end{eqnarray}
Here, to obtain $\phi_{\omega_\ell}(b)$ and its derivative in $r=b$, we need to solve numerically the Eq.~\eqref{H_Radial_equation} inside the star and to continue the solution outside, up to $r=b$, by solving the Regge-wheeler equation.

It is important to note that, the \textit{continued fraction method} applies to three-term recurrence relations. Leins~\emph{et al.} and BBF use the method introduced by Leaver in
the case of Reissner-Nordst\"om black holes \cite{Leaver:1990zz} to reduce four-term recurrence relations (as in \eqref{Recurrence_4_terms}) to three-term recurrence relations by using the gaussian elimination step.

@@

Figure \ref{fig:rp1} shows the Regge pole spectrum for a neutron-star-like body ($R/M = 6$). We see that there are two branches of Regge poles in the first quadrant, which meet at $\text{Re}( \lambda_n(\omega) ) \sim \omega b_0$, where $b_0$ is the impact parameter for the null ray which grazes the surface of the compact body. The axial GW $s=2$ modes (filled markers) are typically close to their scalar-field $s=0$ counterparts (unfilled markers), as might be anticipated from the similarities in the effective potentials for the two cases (see Fig.~\ref{fig:Veff}). \tom{We find no evidence of Regge poles in the fourth quadrant when $\omega>0$. For $\omega<0$ we find that $\lambda_n(-\omega) = \lambda_n(\omega)$. The contour integral deformation means we do not consider poles in the second and third quadrants (for Mohamed: I propose we do not go into more detail about this and the choice of boundary condition...but I am happy to be over ruled!)}

@@

We can be confident that there are no additional branches of Regge poles in the first or fourth quadrants, for two reasons. First, we have scanned across the complex-$\lambda$ domains shown in Figs.~\ref{RP_R6_approx_2Mw_3_6_s_1} and \ref{RP_R226_approx_2Mw_3_6_s_1}, as detailed in Sec.~\ref{subsec:method}. Second, in our calculation of $d\sigma/d\Omega$, we find a precise numerical agreement between the CAM calculation and the partial-wave calculation; this would not be the case if poles in this domain had been missed.
